Boundary Labeling for annotated documents

### 2018-01-23 LaTeX/Paper.tex
Paper:Added suggested changes to section 2.1. Program: No changes.

These restrictions are implemented as follows: We divided the text $T$ into separate lines $L=\{W,H\}$ which are in turn made up of words $W$ and whitespace $H$. Each word $w \in W$ is surrounded by a bounding rectangle $r$, %Definition schreiben?
which marks the space leaders aren't allowed to cross. For a graphical representation see Fig.~\ref{fig:wbound}.

@@

Since we only allowed the Usage of O- and P-Segments in leaders, the only way for a leader to cross through a line of text is with a P-Segment through whitespace, whereas O-Segments are only usable between lines. Therefore, we can create a routing graph $G=\langle V,E\rangle$ whose Edges $E$ reflect the legal paths a leader can take within $T$.
For each whitespace character $w \in W$, one vertex is placed above and below, so that it has the maximum distance from both of its adjacent lines. The start and end of each line also recieve a pair of vertices each. Sites will be represented by the insertion of additional vertices at appropriate places. The edges between the vertices are all perfectly horizontal or vertical, and do neither intersect with any bounding rectangle, nor any vertices other than their starting and ending vertex.The resulting graph looks similar to Fig.~\ref{fig:rgraph}.

>>>>

These restrictions are implemented as follows: We divided the text $T$ into separate lines $L=\{W,H\}$ which are in turn made up of words $W$ and whitespace $H$. The remaining space between lines shall be defined as $S(l_1, l_2)$%improve on this!
with $l_1,l_2 \in L$ and will have no restrictions regarding leader placement. For each word $w \in W$, we define $R(w)$  as its bounding rectangle, which marks the space leaders aren't allowed to cross. For a graphical representation see Fig.~\ref{fig:wbound}.

@@

Since we only allowed the Usage of O- and P-Segments in leaders, the only way for a leader to cross through a line of text is with a P-Segment through whitespace, whereas O-Segments are only usable between lines. Therefore, we can create a routing graph $G=\langle V,E\rangle$ whose Edges $E$ reflect the legal paths a leader can take within $T$.
For each whitespace character $w_x \in W$ in a given line $l_i \in L$, one vertex is placed in $S(l_{i-1},l_i)$ and $S(l_i,l_{i+1})$ each, located above or below the whitespace character, and with a maximum distance from each of its neighbouring lines. The start and end of each line also recieve a pair of vertices each. Sites will be represented by the insertion of additional vertices in $S(l_i, l_{i-1})$ on a similar height as those next to whitespace of the same line and located directly above the center point of its words $w_j$ bounding rectangle $R(w_j)$. Should either $l_{i-1}$ or $l_{i+1}$ not exist, the vertices' vertical placement will be similar to that of the previous or following line. The edges between the vertices are all perfectly horizontal or vertical, and do neither intersect with any bounding rectangle, nor any vertices other than their starting and ending vertex. The resulting graph looks similar to Fig.~\ref{fig:rgraph}.
